Diseñññññññññññño de reactores nucleares \HgA

### 2010-08-31 1tp/paper.tex
avances en el paper

%
% Latex example file for postgrads (04/10/03)
%
% If you have questions please email me: 
%
% M.L.Balogh@durham.ac.uk
%
% or find me in room OC312.
%
% you can copy this file and others from :
%
% http://star-www.dur.ac.uk/~balogh/latex/
%
% Note you can get Latex style files etc. from http://www.ctan.org

% 2. The aastex class file includes some useful astronomy definitions,
% for example special math symbols that are commonly used.  Use
% emulateapj instead to make Apj format.
% YOU SHOULD REMOVE THE TABLE OF
% CONTENTS PAGE WHEN USING APJ FORMAT.
%
%\documentclass[11pt,a4paper]{aastex}
\documentclass[11pt,a4paper]{emulateapj}
\bibliographystyle{apj}

%define general packages
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{natbib}
% spanish packages
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}

@@

\title{Diseño de reactores nucleares \HgA}
\author{Harald Kuntschner \& Michael Balogh}
\date{\today}

\begin{abstract}
This is a sample document which demonstrates some of the basic features
of \LaTeX.  You can easily reformat it for different document or bibliography styles.
\end{abstract}

@@

%Section heading
\section{Introduction}
This file is an example of how to use \LaTeX.  In principle, you only have to worry
about the text content; formatting is taken care of by the options and arguments of
the ``$\backslash$documentclass'' command (other style files are available on the Web;
see \S\ref{sec-webrefs}).  In practice, however, things are not so simple.  Things like
figures and bibliographies can go all wrong when you change styles, so expect to have
to fiddle!

\section{Examples}

@@

Here are some examples of the different ways you can reference a source with the
{\it natbib.sty} style file.  See the header of that file for more options.
\begin{itemize}
\item A first attempt to model this was made by \citet{bar96}.
\item This did not agree with earlier models \citep{bar96}.
\item There are several models for this phenomenon \citep{bar96,bau96}
\item There are several models for this phenomenon \citep[e.g., ][]{bar96,bau96,bure96}
\item Our model is better \citep[Fig. 5]{bau96}.
\item I want to do the references myself! (Baugh et al. 1996)\nocite{bau96}.
\end{itemize}
%
% References
%
\bibliography{example}

>>>>

%
% Latex example file for postgrads (04/10/03)
%
% If you have questions please email me: 
% M.L.Balogh@durham.ac.uk
% or find me in room OC312.
%
% Note you can get Latex style files etc. from http://www.ctan.org

% Use emulateapj instead to make Apj format.
% YOU SHOULD REMOVE THE TABLE OF
% CONTENTS PAGE WHEN USING APJ FORMAT.
\documentclass[11pt,a4paper]{emulateapj}
\bibliographystyle{apj}

%define general packages
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{natbib}

% spanish packages
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\languageshorthands{none}
\noextrasspanish
\let\layoutspanish\relax
\usepackage[spanish]{babel}
\renewcommand\shorthandsspanish{}

@@

\submitted{Departamento Ing. en Informática, ITBA}
\title{Diseñññññññññññño de reactores nucleares \HgA}
\author{Williams M. \& Aráoz M.}
\date{\today}

\begin{abstract}
Entre 2 y tres oraciones.
This is a sample document which demonstrates some of the basic features
of \LaTeX.  You can easily reformat it for different document or bibliography styles.
\end{abstract}

@@

\section{Introduccción}
This file is an example of how to use \LaTeX.  In principle, you only have to worry
about the text content; formatting is taken care of by the options and arguments of
the ``$\backslash$documentclass'' command (other style files are available on the Web;
see \S\ref{sec-webrefs}).  In practice, however, things are not so simple.  Things like
figures and bibliographies can go all wrong when you change styles, so expect to have
to fiddle!

\section{Sección 2}

@@

Here are some examples of the different ways you can reference a source with the
{\it natbib.sty} style file.  See the header of that file for more options.
\begin{itemize}
\item A first attempt to model this was made by \citet{bar96}.
\item This did not agree with earlier models \citep{bar96}.
\item There are several models for this phenomenon \citep{bar96,bau96}
\item There are several models for this phenomenon \citep[e.g., ][]{bar96,bau96,bure96}
\item Our model is better \citep[Fig. 5]{bau96}.
\item I want to do the references myself! (Baugh et al. 1996)\nocite{bau96}.
\end{itemize}

\section{Conclusiones}
Acá poner conclusiones, OBLIGATORIAMENTE
%
% References
%
\bibliography{paper}
